Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-04 demystify.tex
updates

While this document can be useful for all students interested in CS PhD in the US, it is primarily intended for \text bf{international students} from \textbf{smaller countries and less well-known universities} (similarly, for domestic students from universities with no PhD programs or limited research experiences).  
This document aims to level the playing field by providing information that is not readily available to these students.

@@

\paragraph{Grades} Having good GPA is good. However if your school is not well-known, having top grades or rankings
usually will not help because we cannot evaluate them.  This can be an issue for students in many top international universities where the competition is so high that very good students can still have low rankings from these schools (and be overlooked by the adcom).

>>>>

While the information presented here can be useful for all students interested in CS PhD in the US, this guideline is primarily intended for \textbf{international students} from \textbf{smaller countries and less well-known universities} (similarly, for domestic students from universities with no PhD programs or limited research experiences).  
My goal is to level the playing field by providing information that is not readily available to such students.

@@

\paragraph{Grades} Having a good GPA is good. However if your school is not well-known, having top grades or rankings
usually will not help because we cannot evaluate them.  This can be an issue for students in many top international universities where the competition is so high that very good students can still have low rankings from these schools (and be overlooked by adcom).
